### 2021-05-14 Modules/sec_stability.tex
After Israel's comments
Acronyms added

As a preliminary to the following performance discussion in Sec.~\ref{sec_Performance}, we start with simple temporal simulations of the feedback beamformer.
In this section, we start by identifying the unknown parameters in the experimental scenario and formulate their related error terms.
Using those error terms, some basic simulation scenarios are defined, raging from ideal to fully noised cases, which enable rigorous presentation of our findings.
After the error terms have been defined, we first address the temporal stability of the system and discuss its correspondence with the system's response which was found in \eqref{eqn:GeneralFeedbackTransferFunction}.

@@

The analogy of the feedback beamformer to the temporal IIR architecture raises some fundamental questions that should be addressed.

@@

\par The first question, related to the feedback beamformer's analogy to the temporal IIR architecture, is stability related.

@@

To this end, the gain mismatch

@@

    r=g/\hat{g}

@@

and plug \eqref{eq:alpha_beta_opt} into \eqref{eqn:GeneralFeedbackTransferFunction}, giving rise to

@@

            \frac{r}{N}\vecnot{d}^{H}\vecnot{d}
            1 - \frac{r}{N}\vecnot{d}^{H}\vecnot{d}
            = & \frac{r}{1-r}.

@@

As anticipated from \eqref{eq:SF_CB_gainMismatch} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r>1$ the system is not stable, for the received amplitude may increase (in absolute value) to infinite values.

@@

This issue will have to be taken into consideration when one designs such an array for practical applications but is outside the scope of this work.

@@

    Simulating a 3 element ULA based feedback beamformer, steered to a target which resides in the direction $\theta_{s} = \pi/2$ and plotting temporal response (dB) for multiple $r$ values.

@@

            \put (100, 26.5){\rotatebox{0}{$t=5\cdot\tau_{pd}$}}
            \put (100, 14){\rotatebox{0}{$t=10\cdot\tau_{pd}$}}

@@

    Simulation of same setup as in Fig.\ref{fig_stability} with $r=9$.

@@

@@

    After simulating same setup of Fig.\ref{fig_stability} for a fined grid of $r$, we plot the final received amplitude in dB with respect to $r$.

@@

\par The Second question to be asked regards the settling time of the system, for in Fig.~\ref{fig_stability} we easily observe that the settling time of $r=0.6$ (i.e. $\sim{}10$ signal round trips) is substantially shorter than its matching value ($\sim{}50$) when $r=0.9$.
To better understand the phenomenon, we plot the settling time's $r$ dependency in Fig.~\ref{fig_stabilityDur}.

@@

\par Although many interesting questions rise from the initial simulations, most of them are outside the scope of this work.
We choose to add one more note, regarding the influence of the array's number of elements.
Although in spatial processing literature, enlarging the number of elements in the array commonly increases the spatial performance, both examining \eqref{eq:SF_CB_gainMismatch} and simulating the experimental scenarios show that it (increase of elements) does not affect the temporal performance of the system - i.e. the settling time remains the same as $N$ increases.

@@

Using the same weights $\vecnot{\beta}_{\text{CB,opt}},\vecnot{\alpha}_{\text{CB,opt}}$, we denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.

@@

        {\sin{\rBrace{\Delta\theta/2}}},

@@

we define Dirichlet kernel (illustrated in Fig.~\ref{fig_DirichletKernel}) as

@@

D_{\test{orig}}\rBrace{x,N}\triangleq\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}

@@

and the normalized Dirichlet kernel (illustrated in Fig.~\ref{fig_DirichletKernelNorm})
\D{x}{N}=\frac{1}{N}D_{\test{orig}}\rBrace{x,N}=\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}.
Now, \eqref{eqn:GeneralFeedbackTransferFunction} takes the form of

@@

        = &\frac{r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}.

@@

        tics=10,trim=0 0 0 0]{./Media/DirichletKernels.png}
            \put (3, 26){\rotatebox{90}{$D_{\test{orig}}\rBrace{x,N}$}}
            \put (91, 32){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,2}$}}}
            \put (91, 53){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,5}$}}}
            \put (91, 59){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,7}$}}}
            \put (91, 8){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,10}$}}}
    Few illustrations of the Dirichlet kernel, for $N$ values of 2,5,7 and 10.
    \label{fig_DirichletKernel}

>>>>

As a preliminary, we start with simple temporal simulations of the feedback beamformer.
% In this section, we start by identifying the unknown parameters in the experimental scenario and formulate their related error terms.
% Using those error terms, some basic simulation scenarios are defined, raging from ideal to fully noised cases, which enable rigorous presentation of our findings.
% After the error terms have been defined, 
We first address the temporal stability of the system and discuss its correspondence with the system's response which was found in \eqref{eqn:GeneralFeedbackTransferFunction}.

@@

The analogy of the FB to the temporal IIR architecture raises some fundamental issues that should be addressed.

@@

\par The first question, related to the FB's analogy to the temporal IIR architecture, is stability related.

@@

To this end, the gain mismatch is

@@

    r=g/\hat{g}.

@@

And plugging \eqref{eq:alpha_beta_opt} into \eqref{eqn:GeneralFeedbackTransferFunction}, gives rise to

@@

            % = &\frac{    
            % \frac{r}{N}\vecnot{d}^{H}\vecnot{d}
            % }{
            % 1 - \frac{r}{N}\vecnot{d}^{H}\vecnot{d}
            % }\\
            = & \frac{r}{1-r} \triangleq H_{0}.

@@

As anticipated from \eqref{eq:SF_CB_gainMismatch} and confirmed with the simulations presented in Fig.\ref{fig_stability}, for $r\geq1$ the system is not stable, for the received amplitude may increase (in absolute value) to infinite values.

@@

This issue will have to be taken into consideration when one designs such an array for practical applications but currently this is outside the scope of this work.

@@

    Simulating a 3 element ULA based FB, steered to a target which resides in the direction $\theta_{s} = \pi/2$ and plotting temporal response (dB) for multiple $r$ values.

@@

            \put (100, 22.5){\rotatebox{0}{$t=5\cdot\tau_{pd}$}}
            \put (100, 12){\rotatebox{0}{$t=10\cdot\tau_{pd}$}}

@@

    Simulation of the same setup as in Fig.\ref{fig_stability} with $r=0.9$.

@@

    This convergence is analogous to the settling time of the IIR filters' temporal response, where at early stages, the response is not yet in its steady-state.  

@@

    After simulating the same setup as in Fig.\ref{fig_stability}, we plot the final received amplitude in dB with different choices of $r$.

@@

\par The second question to be asked regards the settling time of the system, for in Fig.~\ref{fig_stability} we easily observe that the settling time of $r=0.6$ (i.e. $\sim{}10$ signal round trips) is substantially shorter than its matching value ($\sim{}50$) when $r=0.9$.
To better understand the phenomenon in Fig.~\ref{fig_stabilityDur}, we plot for each $r$ value, its corresponding settling time.

@@

% \par To conclude this section, we choose to add one more note, regarding the influence of the array's number of elements.
% Although in spatial processing literature, enlarging the number of elements in the array commonly increases the spatial performance, both examining \eqref{eq:SF_CB_gainMismatch} and simulating the experimental scenarios show that it (increase of elements) does not affect the temporal performance of the system - i.e. the settling time remains the same as $N$ increases.

@@

\label{subsec_error_trms}
% Using the same weights $\vecnot{\beta}_{\text{CB,opt}},\vecnot{\alpha}_{\text{CB,opt}}$, 
We denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.

@@

        {\sin{\rBrace{\Delta\theta/2}}}

@@

and using the definition of the normalized Dirichlet kernel (illustrated in Fig.~\ref{fig_DirichletKernelNorm})

@@

\D{x}{N}
% =\frac{1}{N}D_{\test{orig}}\rBrace{x,N}
=\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}},

@@

we find that for ULA, \eqref{eqn:GeneralFeedbackTransferFunction} may be expressed as

@@

        H_{\vecnot{\beta}_{\text{CB}},\vecnot{\alpha}_{\text{CB}}}
        = &\frac{r\D{\dTheta/2}{N}\exp\cBrace{-j\vBrace{\dPhi+\rBrace{N-1}\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\cBrace{-j\vBrace{\dPhi+\rBrace{N-1}\dTheta/2}}}.

@@

% \begin{figure}[t!]
%     \begin{center}
%         \begin{overpic}[width=0.65\linewidth, 
%         %grid, 
%         tics=10,trim=0 0 0 0]{./Media/DirichletKernels.png}
%             \put (3, 26){\rotatebox{90}{$D_{\test{orig}}\rBrace{x,N}$}}
%             \put (91, 32){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,2}$}}}
%             \put (91, 53){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,5}$}}}
%             \put (91, 59){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,7}$}}}
%             \put (91, 8){\rotatebox{0}{\scriptsize{$D_{\test{orig}}\rBrace{x,10}$}}}
%             \put (50, 2.5){\rotatebox{0}{$x$}}
%             \put (12, 5){\rotatebox{0}{$-\pi$}}
%             \put (29, 5){\rotatebox{0}{$-\frac{\pi}{2}$}}
%             \put (70, 5){\rotatebox{0}{$\frac{\pi}{2}$}}
%             \put (89, 5){\rotatebox{0}{$\pi$}}
%         \end{overpic}
%     \end{center}
%     \caption{
%     Few illustrations of the Dirichlet kernel, for $N$ values of 2,5,7 and 10.
%     }
%     \label{fig_DirichletKernel}
% \end{figure}

### 2021-05-14 Modules/stabilityEnhancement_freqPairApproach.tex
Acronyms added

\subsection{Intuition}
Bearing in mind that the system's phase alignment sensitivity resides in \eqref{eq_narmalized_pattern} via the  term $\exp\Brack{j\dPhi}=\exp\Brack{j\omega\Delta\tau_{pd}}$ and that the round-trip delay ($\tau_{pd}$) cannot be controlled, one may suggest to use lower frequencies. 
Unfortunately, aiming for practical range estimation errors, the transmission of such low frequencies is physically unfeasible.
As the medium for the wave's propagation in the context of localization is not free space, physical considerations are to be taken when choosing the frequency band of use.
Following the thorough spectrum use overview in \cite{barclay2003propagation}, among the notable considerations for choosing frequency in localization related schemes are
\begin{itemize}
    \item \textbf{Propagation efficiency}\\
    Due to the chemical structure of the atmosphere, some frequencies are propagated efficiently while other are absorbed \cite{wen2015foundations} by the atmosphere layers, being unsuitable for localization applications such as RADAR.
    \item \textbf{Antenna length}\\
    As described in \cite{barclay2003propagation}, although low ($<30_{\text{KHz}}$) frequencies propagate efficiently in the earth-atmosphere wave guide \cite{wen2015foundations}, the wavelength is large ($\sim10_{\text{Km}}$), hence the needed antenna length is too large for any practical use.
    \item \textbf{Signal bandwidth}\\
    As the carrier signal's frequency decreases, so does the available bandwidth due to aliasing.
\end{itemize}
Henceforth, we suggest simultaneous transmission of several frequencies instead of the unfeasible option of transmitting low frequencies. 
In the following we suggest a dual frequency (DF) waveform, utilizing two harmonics, $\omega_1$ and $\omega_2$, and show that range error sensitivity may be resolved  as it will depend on the frequency difference $\omega_{1}-\omega_{2}$.

\subsection{Suggested processing scheme}
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.65\linewidth, 
        % grid, 
        tics=10,trim={0 0 0 0}]{./Media/SpatialIIR_APP.png}
            \put (12.5, 64){$\text{FB}_{\vAlphaI{1},\vBetaI{1}}$}
            \put (61, 64){$\text{FB}_{\vAlphaI{2},\vBetaI{2}}$}
            \put (4.5, 59){$z_{1}\rBrace{t}$}
            \put (54, 59){$z_{2}\rBrace{t}$}
            \put (12.9, 41.5){$\text{BPF}_{\omega_{1}}$}
            \put (61.65, 41.5){$\text{BPF}_{\omega_{2}}$}
            \put (6, 51.5){+}
            \put (55, 51.5){+}
            \put (16, 51.5){\footnotesize{$\text{n}_{1}\rBrace{t}$}}
            \put (64.75, 51.5){\footnotesize{$\text{n}_{2}\rBrace{t}$}}
            \put (24.5, 59){\footnotesize{$\Tx{}_{1}\rBrace{t}$}}
            \put (73.5, 59){\footnotesize{$\Tx{}_{2}\rBrace{t}$}}
            \put (36.25, 64){\scriptsize{$s_{1}\rBrace{t}$}}
            \put (43, 64){\scriptsize{$s_{2}\rBrace{t}$}}
            \put (18.75, 13){\footnotesize{Harmonic mean}}
            \put (32, 2){$Z_{\text{DF}}$}
            \put (54.75, 24){$\Sigma$}
            \put (22, 25){\footnotesize{$\mathcal{F}_{\omega_{1}}$}}
            \put (30.75, 25){\footnotesize{$\mathcal{F}_{\omega_{2}}$}}
        \end{overpic}
    \end{center}
    \caption{Dual-frequency beamformer, consisting of two independent FB blocks and narrowband bandpass filters. The blocks marked by $\mathcal{F}_{\omega_{i}}$ compute the Fourier coefficients in $\omega_{i}$ and their outputs feed the harmonic mean calculator, which generates the DF beamformer's output.}
    \label{fig_app}
\end{figure}
In Fig.~\ref{fig_app}, we demonstrate the use of two independently configured FB instances (see also Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), where each instance is designed to treat a specific frequency band.
A bandpass filter $\text{BPF}_{\omega_{i}},\;i=1,2$ filters a narrowband slice around $\omega_{i}=2\pi f_i$. These filters are used to generate both the transmitted feedback signal ($\text{Tx}_{i}$) and the outputs $z_{i}$. 
The inputs $s_{i}(t) = \exp\Brack{j\omega_{i}t}$  are the two narrowband stimuli signals and $\text{n}_{i}(t)$ represents the additive noise.

@@

    \vBetaCI{1}=\frac{-\vdHatIC{1}\exp\rBrace{j\rBrace{\phiIHat{1}-\phiIHat{2}}}}{\hat{\gI{1}}\norm{\vdHatI{1}}^2}.

@@

With this choice, and similarly to \eqref{eq_narmalized_pattern}, \eqref{eqn_H_DF_general} becomes

@@

For close frequencies, one may assume that $r_{1}\approx{}r_{2}$, hence $\kappa$ tends towards unity, thus significantly mitigating the gain mismatch effect even when both feedback beamformers are mismatched.

@@

In Fig.~\ref{fig_dualfreq_perfectAlignLowSnr}, we repeat the simulation while adding white Gaussian noise to the output of each feedback beamformer. Evidently, even in the noisy case, the DF beamformer achieves a close-to-ideal beampattern, while the SF beamformer suffers from severe distortions.

@@

    \caption{Simulating a 3 element ULA with $r_1=0.6^{2},\; r_2=0.6$ (hence $\kappa=0.6$), assuming an infinite SNR. For each target direction $\thetaD$, the DF beamformer output $Z_\text{DF}$ is evaluated where the beamformer is set to enhance signals impinging from $\thetaD=\pi/2$. 

@@

    The single frequency (SF) beamformer (red squares) and the dual-frequency (DF) solution (green diamonds) are compared to the ideal response  $\Delta{}R_{\text{rt}}=0$ (blue dots) as a reference. 

@@

            \put (16,52){\scriptsize{$\text{SNR}=6_{dB}$}}
            \put (74,52){\scriptsize{$\text{SNR}=0_{dB}$}}
            \put (44.5,12){\scriptsize{$\text{SNR}=-6_{dB}$}}

>>>>

\subsection{Intuition}
Bearing in mind that the system's phase alignment sensitivity resides in \eqref{eq_narmalized_pattern} via the  term $\exp\Brack{j\dPhi}=\exp\Brack{j\omega\Delta\tau_{pd}}$ and that the round-trip delay ($\tau_{pd}$) cannot be controlled, one may suggest to use lower frequencies. 
Unfortunately, aiming for practical range estimation errors, the transmission of such low frequencies is physically unfeasible.
% As the medium for the wave's propagation in the context of localization is not free space, physical considerations are to be taken when choosing the frequency band of use.
Following the thorough spectrum use overview in \cite{barclay2003propagation}, among the notable considerations for choosing frequency in localization related schemes are
\begin{itemize}
    \item \textbf{Propagation efficiency}\\
    Due to the chemical structure of the atmosphere, some frequencies are propagated efficiently while other are absorbed \cite{wen2015foundations} by the atmosphere layers, being unsuitable for localization applications such as RADAR.
    \item \textbf{Antenna length}\\
    As described in \cite{barclay2003propagation}, although low ($<30_{\text{KHz}}$) frequencies propagate efficiently in the earth-atmosphere wave guide \cite{wen2015foundations}, the wavelength is large ($\sim10_{\text{Km}}$), hence the needed antenna length is too large for any practical use.
    \item \textbf{Signal bandwidth}\\
    As the carrier signal's frequency decreases, so does the available bandwidth.
\end{itemize}
Henceforth, we suggest simultaneous transmission of several frequencies instead of the unfeasible option of transmitting low frequencies. 
In the following we suggest a dual frequency (DF) waveform, utilizing two harmonics, $\omega_1$ and $\omega_2$, and show that range error sensitivity may be resolved  as it will depend on the frequency difference $\omega_{1}-\omega_{2}$.

\subsection{Suggested processing scheme}
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.65\linewidth, 
        % grid, 
        tics=10,trim={0 0 0 0}]{./Media/SpatialIIR_APP.png}
            \put (12.5, 64){$\text{FB}_{\vAlphaI{1},\vBetaI{1}}$}
            \put (61, 64){$\text{FB}_{\vAlphaI{2},\vBetaI{2}}$}
            \put (4.5, 59){$z_{1}\rBrace{t}$}
            \put (54, 59){$z_{2}\rBrace{t}$}
            \put (12.9, 41.5){$\text{BPF}_{\omega_{1}}$}
            \put (61.65, 41.5){$\text{BPF}_{\omega_{2}}$}
            \put (6, 51.5){+}
            \put (55, 51.5){+}
            \put (16, 51.5){\footnotesize{$\text{n}_{1}\rBrace{t}$}}
            \put (64.75, 51.5){\footnotesize{$\text{n}_{2}\rBrace{t}$}}
            \put (24.5, 59){\footnotesize{$\Tx{}_{1}\rBrace{t}$}}
            \put (73.5, 59){\footnotesize{$\Tx{}_{2}\rBrace{t}$}}
            \put (36.25, 64){\scriptsize{$s_{1}\rBrace{t}$}}
            \put (43, 64){\scriptsize{$s_{2}\rBrace{t}$}}
            \put (18.75, 13){\footnotesize{Harmonic mean}}
            \put (32, 2){$Z_{\text{DF}}$}
            \put (54.75, 24){$\Sigma$}
            \put (22, 25){\footnotesize{$\mathcal{F}_{\omega_{1}}$}}
            \put (30.75, 25){\footnotesize{$\mathcal{F}_{\omega_{2}}$}}
        \end{overpic}
    \end{center}
    \caption{DF BF, consisting of two independent FB blocks and narrowband bandpass filters. The blocks marked by $\mathcal{F}_{\omega_{i}}$ compute the frequency response at $\omega_{i}$ and their outputs feed the harmonic mean calculator, which generates the DF BF's output.}
    \label{fig_app}
\end{figure}
In Fig.~\ref{fig_app}, we demonstrate the use of two independently configured FB instances (see also Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), where each instance is designed to treat a specific frequency band.
A bandpass filter $\text{BPF}_{\omega_{i}},\;i=1,2$ filters a narrowband slice around $\omega_{i}=2\pi f_i$. These filters are used to generate both the transmitted feedback signal ($\text{Tx}_{i}$) and the outputs $z_{i}$. 
The inputs $s_{i}(t) = \exp\Brack{j\omega_{i}t}$  are the two narrowband stimuli signals and $\text{n}_{i}(t)$ represents the additive noise.

@@

    \vBetaCI{1}=\frac{\vdHatIC{1}\exp\rBrace{j\rBrace{\phiIHat{1}-\phiIHat{2}}}}{\hat{\gI{1}}\norm{\vdHatI{1}}^2}.

@@

With this choice, denoted as the ``DF,CB`` beamformer, and similarly to \eqref{eq_narmalized_pattern}, \eqref{eqn_H_DF_general} becomes

@@

For close frequencies, one may assume that $r_{1}\approx{}r_{2}$, hence $\kappa$ tends towards unity, thus significantly mitigating the gain mismatch effect even when both FBs are mismatched.

@@

In Fig.~\ref{fig_dualfreq_perfectAlignLowSnr}, we repeat the simulation while adding white Gaussian noise to the output of each FB. Evidently, even in the noisy case, the DF BF achieves a close-to-ideal beampattern, while the SF BF suffers from severe distortions.

@@

    \caption{Simulating a 3 element ULA with $r_1=0.6^{2},\; r_2=0.6$ (hence $\kappa=0.6$), assuming an infinite SNR. For each target direction $\thetaD$, the DF BF output $Z_\text{DF}$ is evaluated where the beamformer is set to enhance signals impinging from $\thetaD=\pi/2$. 

@@

    The SF BF (red squares) and the dual-frequency solution (green diamonds) are compared to the ideal response  $\Delta{}R_{\text{rt}}=0$ (blue dots) as a reference. 

@@

            \put (19.75,52){\scriptsize{$\text{SNR}=6_{dB}$}}
            \put (77,52){\scriptsize{$\text{SNR}=0_{dB}$}}
            \put (47.5,12){\scriptsize{$\text{SNR}=-6_{dB}$}}

### 2021-05-14 front/abbrevs.tex
Acronyms added

\abbreviationsAndNotation{
\begin{tabular}{p{2cm}@{:\quad}l}
QED & quod erat demonstratum \\
$c$ & the speed of light \\
$a\pm b$ & the closed interval $\left[a-b,a+b\right]$ \\
\end{tabular}
}

>>>>

\newacronym{DOA}{DOA}{direction of arrival}
\newacronym{RADAR}{RADAR}{dadio Detection And Ranging}
\newacronym{FIR}{FIR}{finite impulse response}
\newacronym{IIR}{IIR}{infinite impulse response}
\newacronym{ULA}{ULA}{uniform linear array}
\newacronym{FIM}{FIM}{fisher information matrix}
\newacronym{SNR}{SNR}{signal to noise ratio}
\newacronym{MUSIC}{MUSIC}{multiple signal classification}
\newacronym{RHS}{RHS}{right hand side}
\newacronym{FB}{FB}{feedback beamformer}
\newacronym{SF}{SF}{single frequency}
\newacronym{DF}{DF}{dual frequency}
\newacronym{HPBW}{HPBW}{half power beamwidth}
\newacronym{PDF}{PDF}{probability density function}
\newacronym{CRLB}{CRLB}{cram\'er Rao lower bound}
\newacronym{CRB}{CRB}{cram\'er Rao bound}
\newacronym{PCA}{PCA}{principal component analysis}
\newacronym{ICA}{ICA}{independent components analysis}
\newacronym{MVDR}{MVDR}{minimum Variance Distortionless Response}
\newacronym{UWB}{UWB}{ultra wide band}
\newacronym{HOS}{HOS}{high order statistics}

\newglossaryentry{VVEC}{name=$\vecnot{v}$,description={A vector}}
\newglossaryentry{VI}{name=$v_{i}$,description={The $i$-th element of vector $\vecnot{v}$}}
\newglossaryentry{VT}{name=$\vecnot{v}^{T}$,description={Transpose of vector $\vecnot{v}$}}
\newglossaryentry{VCONJ}{name=$\vecnot{v}^{*}$,description={Conjugate of vector $\vecnot{v}$}}
\newglossaryentry{VH}{name=$\vecnot{v}^{H}$,description={Hermitian (conjugated) transpose of vector $\vecnot{v}$}}
\newglossaryentry{A}{name=$\vecnot{A}$,description={A Matrix}}
\newglossaryentry{AIJ}{name=$A_{i,j}$,description={The $i,j$-th element of matrix $\vecnot{A}$}}
\newglossaryentry{AT}{name=$\vecnot{A}^{T}$,description={Transpose of matrix $\vecnot{A}$}}
\newglossaryentry{ACONJ}{name=$\vecnot{A}^{*}$,description={Conjugate of matrix $\vecnot{A}$}}
\newglossaryentry{AH}{name=$\vecnot{A}^{H}$,description={Hermitian (conjugated) transpose of matrix $\vecnot{A}$}}
\newglossaryentry{DINTERARRAY}{name=$d$,description={Array's inter-element spacing}}
\newglossaryentry{OMEGA}{name=$\omega$,description={Radial frequency}}
\newglossaryentry{C}{name=$c$,description={Wave's propagation velocity}}
\newglossaryentry{LAMBDA}{name=$\lambda$,description={Wavelength}}
\newglossaryentry{THETAD}{name=$\theta_{d}$,description={Geometrical angle}}
\newglossaryentry{THETA}{name=$\theta$,description={Electrical phase}}
\newglossaryentry{DSTEER}{name=\vecnot{d},description={Steering vector}}
\newglossaryentry{BP}{name=$B$,description={beampattern}}
\newglossaryentry{RANGE}{name=$R$,description={Distance to target}}
\newglossaryentry{ZT}{name=$z\rBrace{t}$,description={Array's temporal output}}
\newglossaryentry{ZW}{name=$Z\rBrace{\omega}$,description={Array's frequency-domain output}}
\newglossaryentry{D}{name=$\mathcal{D}$,description={Directivity}}
\newglossaryentry{HNORM}{name=$\mathcal{H}$,description={Normalized beampattern}}

### 2021-05-14 main/chap_futureResearch.tex
Acronyms added

In the following chapter, some of the many possibilities for further investigation of the feedback beamformer are suggested.
As mentioned in Sec.~\ref{sec_introduceFeedback}, we assumed a single stationary target scenario where the target's location is fixed.
Naturally, the first suggested subjects for future research are dynamic (Sec.\ref{sec_future_dynamic}) and multiple (Sec.\ref{sec_future_multiTarget}) target scenarios.
Another setting which may be an interesting subject for future research is the waveform characteristics (Sec.~\ref{sec_future_wavfrom}) and it's affect on the overall spatial performance.
We choose to conclude with another final suggestion (Sec.~\ref{sec_future_coef}) - i.e. to revisit Sec.\ref{sec_FIM}'s FIM related considerations to the choice of array settings. 
\subsection{Dynamic target}
\label{sec_future_dynamic}
\input{Modules/sec_future_dynamic}
\subsection{Multi-target scenario}
\label{sec_future_multiTarget}
\input{Modules/sec_future_multiTarget}
\subsection{Waveform modifications}
\label{sec_future_wavfrom}
\input{Modules/sec_future_wavfrom}
\subsection{Coefficients quality criteria}
\label{sec_future_coef}
\input{Modules/sec_future_coef}
% \section{Apply to other applications}
% \label{sec_future_applications}
% \input{Modules/sec_future_applications}

>>>>

In the following chapter, some of the many possibilities for further investigation of the FB are suggested.
As mentioned in Sec.~\ref{sec_introduceFeedback}, we assumed a single stationary target scenario where the target's location is fixed.
Naturally, the first suggested subjects for future research are dynamic (Sec.~\ref{sec_future_dynamic}) and multiple (Sec.~\ref{sec_future_multiTarget}) target scenarios.
Another setting which may be an interesting subject for future research is the waveform characteristics (Sec.~\ref{sec_future_wavfrom}) and its effect on the overall spatial performance.
We choose to conclude with another final suggestion (Sec.~\ref{sec_future_coef}) - i.e. to revisit Sec.\ref{sec_FIM}'s FIM related considerations to the choice of array settings. 
\subsection{Dynamic target}
\label{sec_future_dynamic}
\input{Modules/sec_future_dynamic}
\subsection{Multi-target scenario}
\label{sec_future_multiTarget}
\input{Modules/sec_future_multiTarget}
\subsection{Waveform modifications}
\label{sec_future_wavfrom}
\input{Modules/sec_future_wavfrom}
\subsection{Coefficients quality criteria}
\label{sec_future_coef}
\input{Modules/sec_future_coef}
% \section{Apply to other applications}
% \label{sec_future_applications}
% \input{Modules/sec_future_applications}

### 2021-05-14 main/intro.tex
Acronyms added

The array sensors' spatial diversity enables the extraction of spatial information about impinging signals, thus laying the ground for wide range of applications, such as localizing a transmitting source \cite{skolnik2008radar,long2019}, blindly separating mixtures of impinging signals \cite{comon1994independent}, improving signal to noise ratio (SNR) \cite{verdu1998multiuser}, and many more. 
\par A uniform linear array (ULA) has always been a point of interest, due to its simplicity of analysis \cite{van2004optimum,benesty2018}. 
The array size and the number of its elements ($N$) has significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF).

@@

Early research include PCA and errors-in-variables time series analysis \cite{krim1996two}.   

@@

\par A less practical, but optimal in the sense of RMSE \cite{krim1996two}, is the maximum likelihood (ML) approach which tries to find the most probable DOA assuming a known PDF.

@@

Adding the fact that sub-optimal methods such as MUSIC were proven to achieve the CRB under some practical assumptions (e.g. non-coherent signals) \cite{stoica1989music}, these sub optimal estimators are substantially more common in practice. 

@@

We aim to guide the reader thorough the key stages of the research where in each stage, a sufficient background is provided followed by the solution composition.
\par As this research does not closely follows any former work, some of analysis must be rigorously justified, hence we turn to classic literature as guidance.
As an example, for the configuration of the array, we use the Fisher Information Matrix (FIM) aiming to maximize the residing spatial information in the system.
\par After presenting the basic approach with it's complementary adjusted classic spatial analysis, we find that it is inherently sensitive to range estimation errors.
We then suggest a more robust solution which is based on our conclusions from previous analysis.
With the robust solution in hand, we present simulations and compare it to the basic conventional beamformer and the initial more sensitive approach.
As expected, we find that it outperforms them, proving to perform well also in low signal to noise ratios (SNR).

@@

\par In Chapter.~\ref{chap:firstchap} the basic feedback beamformer is presented and thoroughly analysed, followed by the presentation of the more robust architecture, which uses the former as a building block.

>>>>

The array sensors' spatial diversity enables the extraction of spatial information about impinging signals, thus laying the ground for wide range of applications, such as localizing a transmitting source \cite{skolnik2008radar,long2019}, blindly separating mixtures of impinging signals \cite{comon1994independent}, improving SNR \cite{verdu1998multiuser}, and many more. 
\par The ULA has always been a point of interest, due to its simplicity of analysis \cite{van2004optimum,benesty2018}. 
The array size and the number of its elements ($N$) have significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF).

@@

Early research includes PCA and errors-in-variables time series analysis \cite{krim1996two}.

@@

\par A less practical, but optimal in the sense of root mean square error (RMSE) \cite{krim1996two}, is the maximum likelihood (ML) approach which tries to find the most probable DOA assuming a known PDF.

@@

Adding the fact that sub-optimal methods such as MUSIC were proven to achieve the Cram\'er Rao bound (CRB) under some practical assumptions (e.g. non-coherent signals) \cite{stoica1989music}, these sub optimal estimators are substantially more common in practice. 

@@

The reader may observe that the presented research stages lead one to the other as each analysis of the proposed methods uncovered issues that are addressed in the following.
\par
First, as in the early stages of the research, the analogy between a spatial (the ULA) and temporal (the FIR) processors, led us to search for the spatial counterpart of another temporal (the IIR) processor, aiming to translate its advantages from the temporal domain to the spatial domain.
Also, classic spatial analysis tools have been gathered to serve as objective tests to the proposed solutions.
\par
In the second part of the research we present the basic spatial architecture, called FB, introducing the concept of spatial feedback.
The array configuration is rigorously justified, e.g. the setting of the coefficients is done with the use of the Fisher Information Matrix (FIM).
Analysis of the spatial structure proves that the desired recursive spatial response is achievable and we show that the advantages of the proposed solution may be expressed with the classic analysis framework.
As we aim to present a practical architecture, estimation errors were taken into consideration and unveiled some sensitivities that should have been addressed.
\par
After close inspection, we conclude in the third part that the carrier frequencies cause this sensitivity and search for ways to mitigate it.
To this end, we present a more sophisticated design, based on the basic architecture, achieving a practical low sensitivity spatial processor which successfully extracts spatial information from two independent close frequency FB units.
We then simulate the proposed solution and find that in addition to its low sensitivity, it also outperforms the classic beamformers, such as the conventional beamformer (CB) in low SNR. 
% In this thesis, we propose a new feedback based beamformer architecture which acts as an actual spatial IIR filter while avoiding any temporal processing to the signal.
% We aim to guide the reader thorough the key stages of the research where in each stage, a sufficient background is provided followed by the solution composition.
% \par As this research does not closely follows any former work, some of analysis must be rigorously justified, hence we turn to classic literature as guidance.
% As an example, for the configuration of the array, we use the Fisher Information Matrix (FIM) aiming to maximize the residing spatial information in the system.
% \par After presenting the basic approach with it's complementary adjusted classic spatial analysis, we find that it is inherently sensitive to range estimation errors.
% We then suggest a more robust solution which is based on our conclusions from previous analysis.
% With the robust solution in hand, we present simulations and compare it to the basic conventional beamformer (CB) and the initial more sensitive approach.
% As expected, we find that it outperforms them, proving to perform well also in low SNR.

@@

\par In Chapter.~\ref{chap:firstchap} the basic FB is presented and thoroughly analysed, followed by the presentation of the more robust architecture, which uses the former as a building block.
